---
title: "Least-angle Regression (LARS)"
author: "Group 5 Overfit Noise: Yahya Hussein, Andrew Farabow, Bryan Nguyen, Jack Jiang, Manning Luo, Shelby Neal"
date: "November 24, 2021"
output: 
  revealjs::revealjs_presentation:
    theme: simple
    highlight: espresso
    widescreen: true
    mathjax: default
    centering: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## History of Lars

- LARS is an algorithm for fitting regressions to high-dimensional data
developed by Bradley Efron, Trevor Hastie, Iain Johnstone and Robert Tibshirani
- 

## Core Concepts 

```{r, echo = TRUE}
summary(cars)
```

## Why Use Lars

```{r}
plot(pressure)
```

## Mathematical Theory

- LARS is related to Forward Selection and based off of Forward Stagewise Regression. 
- Forward Selection, also known as "Forward Stepwise Regression," is an ambitious algorithm that creates a model by selecting the predictors most correlated to the response. 
Downsides?


----

part 2

----

## Baby Example 1
```{r}
plot(pressure)
```

## Baby Example 2
```{r error=FALSE, warning=FALSE, echo=TRUE}
head(mtcars)
attach(mtcars)
```
```{r}
library(lars)
car_x <- mtcars[c(2:11),]

# Using lars function on 
car_lars <- lars(car_x, mpg, type="lar", trace=TRUE, normalize=TRUE, intercept=TRUE)
```


## Lars using Crime
```{r}
plot(pressure)
```

## References
1. https://tibshirani.su.domains/ftp/lars.pdf
2. https://ir.library.louisville.edu/cgi/viewcontent.cgi?article=3487&context=etd
3. https://cran.r-project.org/web/packages/lars/lars.pdf

## Wrap Up 

